Leadership across cultures and contexts

### 2019-10-25 leadership_across_cultures_contexts.Rmd
Working on results

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
load("Leader2.Rdata")
library(pander)
```

@@

The geographic distribution of the cultures in our sample is displayed in Fig. 1, with cultures labeled by mode of subsistence and represented by a symbol proportional to the number of documents that provide ethnographic texts for that culture (for details, see Table S1). The 1212 text records from `r length(unique(leadershipdata::documents$d_ID))` unique documents describing `r length(unique(leader_text2$d_culture))` cultures were generally short, with a median word count of X, a mean of X, and standard deviation of X. The vast majority of text records pertained to male leadership (89.8%, 898 text records) and very few pertained to female leadership (2.5%, 25 text records). In 7 instances (0.7%)textrecordspertain tobothmales and females,and in 69 text records (6.9%) sex was unknown.

@@

For each of the X coded variables, we computed the percentage of text records that provided support, estimating standard errors using a binomial generalized linear mixed effects model with a random intercept for author nested within culture. See FIG.

```{r, echo=FALSE, warning=FALSE, message=F, fig.width=15, fig.height=8}
plot.variable.support
```

Costs and benefits.

```{r, echo=FALSE, warning=FALSE, message=F, fig.width=15, fig.height=8}
plot.variable.support_costs_benefits
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=F)
load("Leader2.Rdata")
library(pander)
```

@@

The geographic distribution of the cultures in our sample is displayed in Fig. 1, with cultures labeled by mode of subsistence and represented by a symbol proportional to the number of documents that provide ethnographic texts for that culture (for details, see Table S1). The `r nrow(leader_text2)` text records from `r length(unique(documents$d_ID))` unique documents describing `r length(unique(leader_text2$d_culture))` cultures were generally short, with a median word count of X, a mean of X, and standard deviation of X. The vast majority of text records pertained to male leadership (`r male_leader_pct`%) and very few pertained to female leadership (`r female_leader_pct`%), with some records not sex-specific.

@@

For each of the X coded variables, we computed the percentage of text records that provided support, estimating standard errors using a binomial generalized linear mixed effects model with a random intercept for author nested within culture. See Figure \@ref(fig:varsupport).

```{r varsupport, fig.width=15, fig.height=8, fig.cap="Support for each coded variable. Blue: percent of text records with evidence of support. Red: percent of cultures with evidence of support."}
plot.variable.support
```

Costs and benefits. See Figure \@ref(fig:varsupportcb).

```{r varsupportcb, echo=FALSE, warning=FALSE, message=F, fig.width=15, fig.height=8}
plot.variable.support_costs_benefits
```

## Principle components analysis
